Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-11-17 paper/main.tex
Added methodology and more on test environment/procedure

Technical procedure, Cython, two persons, test environment, how we test,
GitHub?

@@

%**************************************%
\chapter{Background technologies}
%**************************************%
% FIXME: Find new and better title

@@

\section{Configuration of test environment}

@@

The performance measurements are only performed on the Tahoe client, and not on
the storage servers. We motivated this by looking at the system performance
graphs of the storage nodes during upload and retrieval, where neither the
\ac{CPU}, network, disk or memory usage runs out of capacity. The \ac{CPU} usage
during testing on one of the storage nodes is depicted in Figure
\ref{fig:munin:storagenode}.

@@

>>>>

All work associated with the project has been carried out by the two authors in
cooperation. Code are written using the VIM editor on Ubuntu Linux
driven machines, and version-controlled using the distributed revision control
system Git. All material produced, including this paper, are publicly available
on GitHub\footnote{\url{http://github.com/ruudud/Tahoe-LAFS-with-SHA-3}}.

The \ac{SHA}-3 candidates are tested on the Tahoe-\ac{LAFS} using uploading and
downloading of files on four desktop computers. Various file sizes are used to
simulate different use cases, and to broaden the perspective as to how the
different candidates perform and behaves when implemented in a secure,
distributed file system.

@@

%**************************************%
\chapter{Background technologies}
%**************************************%

@@

\section{Configuration of Test Environment}

Four machines was used as a testing grid, each containing an Intel(R) Core(TM)2
Duo E8300 \ac{CPU} and 4GB of \ac{RAM}. The 32-bit version of Ubuntu Linux
Server Edition 10.04 was the operating system of choice. The installed versions
of other relevant software can be seen in Table \ref{tbl:installedsw}.

\input{tables/installed_software}

@@

The performance measurements were only performed on the Tahoe client, and not on
the storage servers. We motivated this by looking at the system performance
graphs of the storage nodes during upload and retrieval, where neither the
\ac{CPU}, network, disk or memory usage runs out of capacity. The \ac{CPU} usage
during testing on one of the storage nodes is depicted in Figure
\ref{fig:munin:storagenode}.

@@

The tests was carried out as follows, for each of the test vectors:

\begin{itemize}
  \item Upload all files in the same category (as defined shortly) one by one.
  \item Download all files in the same manner.
\end{itemize}

During these operations, we counted the number of hashing operations performed,
and timed total time spent hashing, i.e. the total time it took for the function
calls to the underlying hashing operations to complete.
